\begin{cvenum}
%\item I.~Kwak, D.~Kriegman, and K.~Branson, ``Structured rnns for action start
%  detection,'' {\em arXiv preprint arXiv:????.????}, 2019.

\item J.~Z. Guo, B. Sauerbrei, J. Cohen, M. Mischiatti, A. Graves, K. Branson, and A. Hantman. ``Disrupting cortico-cerebellar communication impairs dexterity'', {\em eLife} 2021;10:e65906, 2021.
  
\item C.~E. Schretter, Y. Aso, M. Dreher, A.~A. Robie, M.-J. Dolan, N. Chen, M. Ito, T. Yang, R. Parekh, K. Branson, and G.~M. Rubin, ``Neuronal circuitry underlying female aggression in {\em {{D}}rosophila}, {\em eLife}, eLife 2020;9:e58942, 2020.
  
\item D.~J. Im, I.~S. Kwak, and K.~Branson, ``Evaluation metrics for behavior modeling,'' arXiv:2007.12298, 2020.
  
\item I.~S. Kwak, D.~Kriegman, and K.~Branson, ``Detecting the starting frame of actions in video,'' {\em WACV}, 2020.

\item B.~Sauerbrei, J.-Z. Guo, M.~Mischiati, W.~Guo, M.~Kabra, N.~Verma, B.~Mensch, K.~Branson, and A.~Hantman, ``Cortical pattern generation during dexterous movements is input-driven,'' {\em Nature}, vol.~577 pp.~386--391, 2019.

\item D.~J. Im, S.~Prakhya, J.~Yan, S.~Turaga, and K.~Branson, ``Importance weighted
  adversarial variational autoencoders for spike inference from calcium imaging
  data,'' {\em CoRR}, vol.~abs/1906.03214, 2019.

\item J.-Z. Guo, B.~Sauerbrei, J.~D. Cohen, M.~Mischiati, A.~Graves, F.~Pisanello,
  K.~Branson, and A.~W. Hantman, ``The pontine nuclei are an integrative
  cortico-cerebellar link critical for dexterity,'' {\em bioRxiv}, 2019.

\item J.~M. Ache, S.~Namiki, A.~Lee, K.~Branson, and G.~M. Card, ``Context-dependent
  decoupling of sensory and motor circuits underlies behavioral flexibility,''
  {\em Nature Neuroscience}, vol.~22, no.~7, 2019.

\item D.~J. Im, N.~Verma, and K.~Branson, ``Stochastic neighbor embedding under
  f-divergences,'' {\em CoRR}, vol.~abs/1811.01247, 2018.

\item Daniel Jiwoong~Im, H.~Ma, G.~W. Taylor, and K.~Branson,
  ``Quantitatively evaluating {GAN}s with divergences proposed for training,''
  in {\em International Conference on Learning Representations},
  2018.

\item K.~McDole, L.~Guignard, F.~Amat, A.~Berger, G.~Malandain, L.~A. Royer, S.~C.
  Turaga, K.~Branson, and P.~J. Keller, ``In toto imaging and reconstruction of
  post-implantation mouse development at the single-cell level,'' {\em Cell},
  vol.~175, no.~3, pp.~859--876, 2018.

\item I.~F. Rodriguez, R.~Megret, R.~Egnor, K.~Branson, J.~L. Agosto, T.~Giray, and
  E.~Acuna, ``Multiple animals tracking in videousing part affinity fields,''
  in {\em Visual Observation and Analysis of Vertebrate And Insect Behavior},
  2018.

\item I.~F. Rodriguez, K.~Branson, E.~Acuna, J.~L. Agosto-Rivera, T.~Giray, and
  R.~Megret, ``Honeybee detection and pose estimation using convolutional
  neural networks,'' in {\em Reconnaissance des Formes, Image, Apprentissage et
  Perception}, 2018.

\item K.~Branson, ``A deep (learning) dive into a cell,'' {\em Nature Methods},
  vol.~15, no.~4, p.~253, 2018.

\item A.~A. Robie, J.~Hirokawa, A.~W. Edwards, L.~A. Umayam,
  A.~Lee, M.~L. Phillips, G.~M. Card, W.~Korff, G.~M. Rubin, J.~H. Simpson,
  M.~B. Reiser, and K.~Branson, ``Mapping the neural substrates of behavior,''
  {\em Cell}, vol.~170, no.~2, pp.~393--406, 2017.

\item R.~Sen, M.~Wu, K.~Branson, A.~Robie, G.~M. Rubin, and B.~J. Dickson,
  ``Moonwalker descending neurons mediate visually evoked retreat in
  {D}rosophila,'' {\em Current Biology}, vol.~27, no.~5, pp.~766--771, 2017.

\item A.~A. Robie, K.~M. Seagraves, S.~R. Egnor, and K.~Branson, ``Machine vision
  methods for analyzing social interactions,'' {\em Journal of Experimental
  Biology}, vol.~220, no.~1, pp.~25--34, 2017.

\item D.~J. Im, M.~Tao, and K.~Branson, ``An empirical analysis of deep network loss
  surfaces,'' {\em CoRR}, vol.~abs/1612.04010, 2016.

\item E.~Eyjolfsdottir, K.~Branson, Y.~Yue, and P.~Perona,
  ``Learning recurrent representations for hierarchical behavior modeling,'' in
  {\em International Conference on Learning Representations},
  2017.

\item S.~R. Egnor and K.~Branson, ``Computational analysis of behavior,'' {\em Annual
  Review of Neuroscience}, vol.~39, pp.~217--236, 2016.

\item J.-Z. Guo, A.~R. Graves, W.~W. Guo, J.~Zheng, A.~Lee,
  J.~Rodriguez-Gonzalez, N.~Li, J.~J. Macklin, J.~W. Phillips, B.~D. Mensh,
  K.~Branson, and A.~Hantman, ``Cortex commands the performance of skilled
  movement,'' {\em e{L}ife}, vol.~4, p.~e10774, 2015.

\item K.~Branson and J.~Freeman, ``Imaging the neural basis of locomotion,'' {\em
  Cell}, vol.~163, no.~3, pp.~541--542, 2015.

\item W.~C. Lemon, S.~R. Pulver, B.~H{\"o}ckendorf, K.~McDole, K.~Branson,
  J.~Freeman, and P.~J. Keller, ``Whole-central nervous system functional
  imaging in larval {\em {{D}}rosophila},'' {\em Nature Communications}, vol.~6, p.~7924,
  2015.

\item T.~Ohyama, C.~M. Schneider-Mizell, R.~D. Fetter, J.~V. Aleman, R.~Franconville, M.~Rivera-Alba, B.~D. Mensh, K.~M. Branson, J.~H. Simpson, J.~W. Truman, {\em et~al.}, ``A multilevel multimodal circuit enhances action selection in {\em {{D}}rosophila},'' {\em Nature}, vol.~520, no.~7549, p.~633, 2015.

\item N.~Verma and K.~Branson, ``Sample complexity of learning mahalanobis distance metrics,'' in {\em Advances in Neural Information Processing Systems}, pp.~2584--2592, 2015.

\item M.~Kabra, A.~Robie, and K.~Branson, ``Understanding classifier errors by
  examining influential neighbors,'' in {\em Computer Vision and Pattern
  Recognition}, June 2015.

\item K.~Branson, ``Distinguishing seemingly indistinguishable animals with computer
  vision,'' {\em Nature Methods}, vol.~11, no.~7, p.~721, 2014.

\item A.~I. Dell, J.~A. Bender, K.~Branson, I.~D. Couzin, G.~G. de~Polavieja, L.~P.
  Noldus, A.~P{\'e}rez-Escudero, P.~Perona, A.~D. Straw, M.~Wikelski, {\em
  et~al.}, ``Automated image-based tracking and its application in ecology,''
  {\em Trends in Ecology \& Evolution}, vol.~29, no.~7, pp.~417--428, 2014.

  \item Y.~Aso, D.~Sitaraman, T.~Ichinose, K.~R. Kaun, K.~Vogt, G.~Belliart-Gu{\'e}rin, P.-Y. Pla{\c{c}}ais, A.~A. Robie, N.~Yamagata, C.~Schnaitmann, W.~J. Rowell, R.~M. Johnston, T.-T~B. Ngo, N.~Chen, W.~Korff, M.~N. Nitabach, U.~Heberlein, T.~Preat, K.~Branson, H.~Tanimoto,G.~M. Rubin,  ``Mushroom body output neurons encode valence and guide memory-based action selection in {\em {{D}}rosophila},'' {\em eLife}, vol.~3, p.~e04580, 2014.

\item F.~Amat, W.~Lemon, D.~P. Mossing, K.~McDole, Y.~Wan, K.~Branson, E.~W. Myers,
  and P.~J. Keller, ``Fast, accurate reconstruction of cell lineages from
  large-scale fluorescence microscopy data,'' {\em Nature Methods}, vol.~11,
  no.~9, p.~951, 2014.

\item D.~G. Tervo, M.~Proskurin, M.~Manakov, M.~Kabra, A.~Vollmer, K.~Branson, and
  A.~Y. Karpova, ``Behavioral variability through stochastic choice and its
  gating by anterior cingulate cortex,'' {\em Cell}, vol.~159, no.~1,
  pp.~21--32, 2014.
  
\item M.~Kabra, A.~A. Robie, M.~Rivera-Alba, S.~Branson, and K.~Branson, ``{{JAABA}}:
  An interactive machine-learning tool for automatic annotation of animal
  behavior,'' {\em Nature Methods}, vol.~10, pp.~64--67, 2013.

\item F.~Zabala, P.~Polidoro, A.~Robie, K.~Branson, P.~Perona, and M.~H. Dickinson,
  ``A simple strategy for detecting moving objects during locomotion revealed
  by animal-robot interactions,'' {\em Current Biology}, vol.~22, no.~14,
  pp.~1344--1350, 2012.

\item A.~D. Straw, K.~Branson, T.~R. Neumann, and M.~H. Dickinson, ``Multi-camera
  real-time three-dimensional tracking of multiple flying animals,'' {\em
  Journal of The Royal Society Interface}, vol.~8, no.~56, pp.~395--409, 2010.

\item K.~Branson, A.~A. Robie, J.~Bender, P.~Perona, and M.~Dickinson,
  ``High-throughput ethomics in large groups of \emph{{D}rosophila},'' {\em
  Nature Methods}, vol.~6, pp.~451--457, 2009.

\item S.~Agarwal, K.~Branson, and S.~Belongie, ``Higher order learning with graphs,''
  in {\em Proceedings of the 23rd international conference on Machine
  learning}, pp.~17--24, ACM, 2006.

\item K.~Branson and S.~Belongie, ``Tracking multiple mouse contours (without too
  many samples),'' in {\em 2005 IEEE Computer Society Conference on Computer
  Vision and Pattern Recognition (CVPR'05)}, vol.~1, pp.~1039--1046, IEEE,
  2005.

\item K.~Branson, V.~Rabaud, and S.~Belongie, ``Three brown mice: See how they run,''
  in {\em In VS-PETS Workshop at ICCV}, Citeseer, 2003.

\item G.~W. Cottrell, K.~M. Branson, and A.~J. Calder, ``Do expression and identity
  need separate representations?,'' in {\em Proceedings of the Annual Meeting
  of the Cognitive Science Society, 24 (24)}, 2002.

\end{cvenum}
