\begin{cvenum}

\item I.~S. Kwak, D.~Kriegman, and K.~Branson, ``Detecting the starting frame of actions in video,'' {\em WACV}, 2020.
  
\item B.~Sauerbrei, J.-Z. Guo, M.~Mischiati, W.~Guo, M.~Kabra, N.~Verma, B.~Mensch, K.~Branson, and A.~Hantman, ``Cortical pattern generation during dexterous movements is input-driven,'' {\em Nature}, vol.~577 pp.~386--391, 2019.

\item D.~J. Im, H.~Ma, G.~W. Taylor, and K.~Branson,
  ``Quantitatively evaluating {GAN}s with divergences proposed for training,''
  in {\em International Conference on Learning Representations},
  2018.
  
\item A.~A. Robie, J.~Hirokawa, A.~W. Edwards, L.~A. Umayam,
  A.~Lee, M.~L. Phillips, G.~M. Card, W.~Korff, G.~M. Rubin, J.~H. Simpson,
  M.~B. Reiser, and K.~Branson, ``Mapping the neural substrates of behavior,''
  {\em Cell}, vol.~170, no.~2, pp.~393--406, 2017.

\item E.~Eyjolfsdottir, K.~Branson, Y.~Yue, and P.~Perona,
  ``Learning recurrent representations for hierarchical behavior modeling,'' in {\em International Conference on Learning Representations}, 2017.

\item S.~R. Egnor and K.~Branson, ``Computational analysis of behavior,'' {\em Annual Review of Neuroscience}, vol.~39, pp.~217--236, 2016.

\item J.-Z.~Guo, A.~R. Graves, W.~W. Guo, J.~Zheng, A.~Lee,
  J.~Rodriguez-Gonzalez, N.~Li, J.~J. Macklin, J.~W. Phillips, B.~D. Mensh,
  K.~Branson, and A.~Hantman, ``Cortex commands the performance of skilled
  movement,'' {\em e{L}ife}, vol.~4, p.~e10774, 2015.

\item N.~Verma and K.~Branson, ``Sample complexity of learning mahalanobis distance metrics,'' in {\em Advances in Neural Information Processing Systems}, pp.~2584--2592, 2015.
  
\item M.~Kabra, A.~Robie, and K.~Branson, ``Understanding classifier errors by
  examining influential neighbors,'' in {\em Computer Vision and Pattern
  Recognition}, June 2015.

\item Y.~Aso, D.~Sitaraman, T.~Ichinose, K.~R. Kaun, K.~Vogt, G.~Belliart-Gu{\'e}rin, P.-Y. Pla{\c{c}}ais, A.~A. Robie, N.~Yamagata, C.~Schnaitmann, W.~J. Rowell, R.~M. Johnston, T.-T~B. Ngo, N.~Chen, W.~Korff, M.~N. Nitabach, U.~Heberlein, T.~Preat, K.~Branson, H.~Tanimoto, and G.~M. Rubin, ``Mushroom body output neurons encode valence and guide memory-based action selection in {\em {{D}}rosophila},'' {\em eLife}, vol.~3, p.~e04580, 2014.

\item F.~Amat, W.~Lemon, D.~P. Mossing, K.~McDole, Y.~Wan, K.~Branson, E.~W. Myers,  and P.~J. Keller, ``Fast, accurate reconstruction of cell lineages from large-scale fluorescence microscopy data,'' {\em Nature Methods}, vol.~11, no.~9, p.~951, 2014.

\item D.~G. Tervo, M.~Proskurin, M.~Manakov, M.~Kabra, A.~Vollmer, K.~Branson, and
  A.~Y. Karpova, ``Behavioral variability through stochastic choice and its
  gating by anterior cingulate cortex,'' {\em Cell}, vol.~159, no.~1,
  pp.~21--32, 2014.
  
\item M.~Kabra, A.~A. Robie, M.~Rivera-Alba, S.~Branson, and K.~Branson, ``{{JAABA}}:  An interactive machine-learning tool for automatic annotation of animal behavior,'' {\em Nature Methods}, vol.~10, pp.~64--67, 2013.
  
\item K.~Branson, A.~A. Robie, J.~Bender, P.~Perona, and M.~Dickinson, ``High-throughput ethomics in large groups of \emph{{D}rosophila},'' {\em Nature Methods}, vol.~6, pp.~451--457, 2009.

\end{cvenum}
